---
title: "p8105_hw6_maf2311"
author: "Mackenzie Frost (maf2311)"
output: github_document
---

December 3, 2022

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

2017 Central Park weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

The boostrap is helpful when you’d like to perform inference for a parameter / value / summary that doesn’t have an easy-to-write-down distribution in the usual repeated sampling framework. We’ll focus on a simple linear regression with tmax as the response and tmin as the predictor, and are interested in the distribution of two quantities estimated from these data:

* r̂ 2
* log(β̂ 0∗β̂ 1)

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words. Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1). Note: broom::glance() is helpful for extracting r̂ 2 from a fitted regression, and broom::tidy() (with some additional wrangling) should help in computing log(β̂ 0∗β̂ 1).

# Problem 2

Homicides in 50 large US cities, Washington Post

```{r 2_import_and_clean}
homicides = read_csv(file = "./data/data-homicides-master/homicide-data.csv", 
    col_types = "cncccncccnnc") %>%
  mutate(
    city_state = str_c(city, ", ", state),
    solved = ifelse((disposition == "Closed without arrest" | disposition == "Open/No arrest"), 0, 1)
  ) %>%
  filter(city_state != "Dallas, TX", city_state != "Phoenix, AZ",city_state != "Kansas City, MO", city_state != "Tulsa, AL") %>%
  filter(victim_race %in% c("White", "Black"))

#test to see if victim_age is numeric = TRUE
is.numeric(homicides$victim_age)
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

# Problem 3

Data on ~4000 children and their birthweight:

```{r 3_import_and_clean}
birthweight = read_csv(file = "./data/birthweight.csv") 

birthweight %>% skimr::skim()
#all variables improted as numeric
#Based on the table output, there is no missing data
```

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.





